\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-28 manuscript.Rnw
Updates using new hesim summary.ce() method

For a given subgroup, QALYs and costs are simulated for each PSA sample, treatment strategy, and health state. They are summarized with the \code{$summarize()} method, which first sums across health states and then computes a (weighted) average across patients, by PSA sample, treatment strategy, and subgroup.

<<ictstm_summarize>>=
ce_sim_ictstm <- ictstm$summarize()
head(ce_sim_ictstm$costs)
@

The output is a generic cost-effectiveness object (of class \code{ce}) that can be used to perform CEA. We demonstrate a formal CEA in Section~\ref{sec:cea}. Here, we make a simple pairwise comparisons between each of the new interventions (New 2 and New 1) and the comparator (SOC), and compute the incremental cost-effectiveness ratio (ICER).

<<ictstm_icer>>=
ce_sim_ictstm <- ictstm$summarize()
cea_pw_ictstm <- cea_pw(ce_sim_ictstm, comparator = 1,
                        dr_qalys = .03, dr_costs = .03,
                        k = seq(0, 25000, 500))
icer_tbl(cea_pw_ictstm, colnames = strategies$strategy_name,
         k = 100000)
@

@@

QALYs and costs are simulated using the same \code{sim_qalys()} and \code{sim_costs()} methods as in the previous section, and the ICER is computed in the same fashion as well.

@@

<<psm_icer>>=
ce_sim_psm <- psm$summarize(by_grp = TRUE)
cea_pw_psm <- cea_pw(ce_sim_psm, comparator = 1,
                     dr_qalys = .03, dr_costs = .03)
icer_tbl(cea_pw_psm, output = "data.table",
         k = 100000)
@

@@

and an ICER is computed.

<<cdtstm_icer>>=
ce_sim_cdtstm <- cdtstm$summarize()
cea_pw_cdtstm <- cea_pw(ce_sim_cdtstm, comparator = 1, 
                        dr_costs = .03, dr_qalys = .03)
icer_tbl(cea_pw_cdtstm, output = "data.table", k = 100000)
@

>>>>

For a given subgroup, QALYs and costs are simulated for each PSA sample, treatment strategy, and health state. They are summarized with the \code{$summarize()} method, which first sums across health states and then computes a (weighted) average across patients, by PSA sample, treatment strategy, and subgroup. The output is a generic cost-effectiveness object (of class \code{ce}) that can be used to perform CEA as demonstrated in Section~\ref{sec:cea}. Here, we use the \code{summary()} method to summarize the results.

<<ictstm_summarize>>=
ce_sim_ictstm <- ictstm$summarize()
summary(ce_sim_ictstm)
@

@@

QALYs and costs are simulated using the same \code{sim_qalys()} and \code{sim_costs()} methods as in the previous section, and the results are summarized in the same fashion as well.

@@

<<psm_icer>>=
ce_sim_psm <- psm$summarize(by_grp = TRUE)
summary(ce_sim_psm)
@

@@

and the results are summarized.

<<cdtstm_icer>>=
ce_sim_cdtstm <- cdtstm$summarize()
summary(ce_sim_cdtstm)
@
